Incremental Faint Object Detection in Multi-Epoch Observations

### 2016-11-02 ms.tex
Added discussion at end of Sxn 4

Figure~\ref{fig:bf2} shows the distribution of Bayes factors, for the real (mock) and noise sources, now including the astrometric cross-matching factor.
Banding due to discreteness in the number of detections is now clearly apparent; the 9 levels correspond to the different number of detections with the lowest being 1.
The Bayes factors for the noise peaks have moved to much lower values, due to the low likelihood of directional coincidences.
For the lowest band, corresponding to a single detectin, $B_{\rm{}pos}$ is unity by definition (no constraint coming from a single detection), producing the same Bayes factor distribution as in the flux-only calculation.

>>>>

Figure~\ref{fig:bf2} shows the distribution of Bayes factors, for the real (mock) and noise sources, now including the astrometric cross-matching factor.
Banding due to discreteness in the number of detections is now clearly apparent among the true-object Bayes factors; the 9 levels correspond to the different number of detections with the lowest being 1.
For the lowest band, corresponding to a single detection, $B_{\rm{}pos}$ is unity by definition (no constraint coming from a single detection), producing the same Bayes factor distribution as in the flux-only calculation.
For multiple detections, the Bayes factors for the true sources are greatly enhanced by including astrometric information (note that the ordinate is logarithmic); just two detections produces quite strong evidence for the true-object hypothesis.
The Bayes factors for the noise peaks have moved to much lower values, due to the low likelihood of directional coincidences.

This computation demonstrates that flux and astrometric catalog data, combined across epochs, can strongly distinguish real objects from spurious detections.
We have not addressed what threshold Bayes factor to use for producing a multi-epoch catalog, or, in Bayesian terms, how to convert Bayes factors into posterior probabilities for candidate objects.
As noted above, when the object population density (on the sky and in flux) is known a priori, the calculation is straightforward (e.g., the prior odds will be proportional to the ratio of true object and noise peak sky densities).
When these quantities are unknown, a possibly complicated hierarchical Bayesian calculation can jointly estimate them and the object properties.
When many objects are detected, an approximate approach, plugging in empirical estimates of the densities based on the data, is likely to suffice, as described in \cite{REF,REF}.
\enote{SCMA5 refs?}
